Highly Available Transactions: Virtues and Limitations

### 2013-03-20 writeup/evaluation.tex
eval

There are several mechanisms that do not provide serializability (and
often provide HAT semantics) but which are not available:

>>>>

There are several mechanisms that do not provide serializability (and
often provide HAT semantics) but which are not
available. Non-serializability can but does not necessarily imply high
availability and low latency:
